### 2023-10-17 2.State/main.tex
finshed preview

\begin{itemize}
\item Vectors are displayed as $\overrightarrow{v}$ and are considered to be vertical matrixes when used in an equation.
\item $\overrightarrow{1}$ represent a vector that only contains ones of variable size.
\item $\odot$ is used for the Hadamart product, that is the point wise multiplication of each element of the matrixes
\item $\cdot$ is used in two cases :
\begin{itemize}
\item When used with a number, it is the product of those numbers.
\item When used with matrixes, it is the matrix product
\end{itemize}
\end{itemize}

>>>>

\begin{itemize}
  \item Vectors are displayed as $\overrightarrow{v}$ and are considered to be vertical matrixes, matrixes of size ($1\times n$) for vector of size $n$.
  \item $\overrightarrow{1}$ represent a vector that only contains ones of variable size.
  \item $\odot$ is used for the Hadamart product, that is the point wise multiplication of each element of the matrixes
  \item $\cdot$ is used in two cases :
    \begin{itemize}
      \item When used with scalars, it is the product of those scalars.
      \item When used with matrixes, it is the matrix product
    \end{itemize}
  \item $+$ is also used in two cases :
    \begin{itemize}
      \item When used with scalars, it is the sum of those scalars.
      \item When used with vectors (column matrixes), it is the point wise sum, basically adding each element to each other. The result is a vector of the same size.
    \end{itemize}
\end{itemize}
